### 2021-10-20 README.rmd
adding codcovr and correcting a minor bug in cat_to_belongings

<!-- badges: start -->
[![R-CMD-check](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml)
```{r echo=FALSE, results='asis'}
cat(
  badge_github_version(color = "green"),
  badge_cran_release(color = "blue"),
  badge_cran_download(color = "blue", type = "grand-total")
)
```
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml)
```{r echo=FALSE, results='asis'}
cat(
  badge_github_version(color = "green"),
  badge_cran_release(color = "blue"),
  badge_cran_download(color = "blue", type = "grand-total")
)
```
[![Codecov test coverage](https://codecov.io/gh/JeremyGelb/geocmeans/branch/master/graph/badge.svg)](https://codecov.io/gh/JeremyGelb/geocmeans?branch=master)
<!-- badges: end -->
